# Reproducible Research: Peer Assessment 1
## Loading and preprocessing the data
```{r}
act <- read.csv("activity.csv", header=TRUE)
act$date <- as.Date(act$date)
```
## What is mean total number of steps taken per day?
```{r}
days <- unique(act$date)
steps <- sapply(days, function(x) sum(act[which(act$date == x), 1]))
plot(days, steps, type="o", main="Total Steps per day")
```
```{r}
aveSteps <- sapply(days, function(x) mean(act[which(act$date == x), 1]))
medSteps <- sapply(days, function(x) median(act[which(act$date == x), 1]))
head(cbind(as.character(days),aveSteps,medSteps))
```
## What is the average daily activity pattern?
```{r}
intervals <- unique(act$interval)
aveInts <- sapply(intervals,
                  function(x) mean(act[which(act$interval == x), 1], na.rm=T))
plot(intervals, aveInts, type="l", main="Average Steps in each time interval")
intervals[which.max(aveInts)]
```
## Imputing missing values
```{r}
length(which(is.na(act$steps)))
actNew <- act
actNew$steps <- sapply(1:nrow(act),
                    function(x) if(is.na(act[x,1]))  ## to replace NAs
                                        aveInts[which(act[x,3] == intervals)]
                                else act[x,1])
stepsNew <- sapply(days,
                   function(x) sum(actNew[which(actNew$date == x), 1]))
par(mfrow=c(2,1))
plot(days, steps, type="o", main="With NAs")
plot(days, stepsNew, type="o", main="with NAs Replaced")
aveStepsNew <- sapply(days,
                      function(x) mean(actNew[which(actNew$date == x), 1]))
medStepsNew <- sapply(days,
                      function(x) median(actNew[which(actNew$date == x), 1]))
```
first 10 rows of new average and mean and old average and mean with NAs
```{r}
head(cbind(aveSteps,aveStepsNew,medSteps,medStepsNew))
```
## Are there differences in activity patterns between weekdays and weekends?
i assume weekends are Sundays and Saturdays.
```{r}
actNew$weekend <- weekdays(act$date) %in% c("Saturday","Sunday")
aveWeekdays <- sapply(intervals,
                      function(x) mean(actNew[which(actNew$interval == x &
                                              !actNew$weekend), 1]))
aveWeekends <- sapply(intervals,
                      function(x) mean(actNew[which(actNew$interval == x &
                                              actNew$weekend), 1]))
par(mfrow=c(2,1))
plot(intervals, aveWeekdays, type="l", ylab="Average Steps", main="Weekdays")
plot(intervals, aveWeekends, type="l", ylab="Average Steps", main="Weekends")
```
it seems that people walk less during week days.
